Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-12-02 R/model_fcs_check.Rmd
Update

---
title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "Markus Bauer^* <br>"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  github_document:
    toc: true
    toc_depth: 2
    dev: jpeg
    fig_width: 12
    fig_height: 12
---

@@

@@

* Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
<br>
[ORCiD ID: 0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
<br>
[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
<br>
[GitHub: markus1bauer](https://github.com/markus1bauer)

@@

```{r collapse = TRUE}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_full.Rdata"))
m_1 <- m2
m_2 <- m_full
m_1$formula
m_2$formula
```

@@

```{r collapse = TRUE}
range(draws1$rhat)
range(draws2$rhat)
```

@@

```{r collapse = TRUE}
range(draws1$ess_bulk)
range(draws2$ess_bulk)
range(draws1$ess_tail)
range(draws2$ess_tail)
```

@@

```{r}
(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```

@@

## Session info

```{r echo = FALSE}
sessionInfo()
```

>>>>

---
title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: jpeg
    fig_width: 12
    fig_height: 7
---

@@

```{r, include=FALSE}
knitr::knit_hooks$set(output = function(x, options){
  if(!is.null(options$max_height)){
    paste('<pre style = "max-height:', options$max_height, '; float: left; width: 910px; overflow-y: auto;">', x, "</pre>", sep = "")
  }else{
    x
  }

})
```

@@

<span>&#42;</span> Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
<br>
ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
<br>
[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
<br>
GitHub: [markus1bauer](https://github.com/markus1bauer)

@@

```{r collapse = TRUE}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_full.Rdata"))
m_1 <- m2
m_2 <- m_full
m_1$formula
m_2$formula
m_1$family
m_2$family
```

@@

```{r collapse = TRUE}
mcmc_rhat(draws1$rhat)
mcmc_rhat(draws2$rhat)
```

@@

```{r collapse = TRUE}
mcmc_neff(neff_ratio(m_1))
mcmc_neff(neff_ratio(m_2))
```

@@

```{r max_height = '100px'}
(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```

@@

# Session info

```{r echo = FALSE, max_height = "100px"}
sessionInfo()
```
